Import data and load packages
The IMDB ratings dataset is used
```{r}
library(ggplot2)
setwd("") #set your working directory
data <- read.csv('MovieRatings.csv') #import the csv file of the dataset

```

Change name of the columns
```{r}
colnames(data) <- c("Film", "Genre", "CriticsRating", "AudienceRating", "BudgetMillions", "Year")

```

Display the first 6 rows of the dataset
```{r}
head(data)
```

Plot statistical transformations (the Critics vs Audience Ratings for the movies and color by Genre)
```{r}
u <- ggplot(data = data, aes(x = CriticsRating, y = AudienceRating, colour = Genre))
u + geom_point() + geom_smooth(fill = NA)
```

Using boxplots for better statistical insights
```{r}
u <- ggplot(data = data, aes(x = Genre, y = AudienceRating, colour = Genre))
u + geom_boxplot(size = 1.2)
```

Using a Jitter plot along with box plot to see the deviation in data points 
```{r}
u + geom_boxplot(size = 1.2) + geom_jitter()
```

Improve the plot by adding transparency
```{r}
u + geom_jitter() + geom_boxplot(size = 1.2, alpha = 0.5)
```